An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-03 scagnostics.Rmd
Small changes only.

[@Grimm2016] explored the behaviour of scagnostics for selecting variables, and proposed two more, based on smoothing splines that have some nicer properties. In addition the availability of another two indices based on information criteria, maximal and total information coefficient (MIC and TIC) [@Reshef1518] round out our collection of metrics. \footnote{It is interesting to note that entropy, closely related to the notion of mutual information, has previously been considered as a projection pursuit index when searching for interesting one-dimensional projections, see \cite{nason1992}, \cite{NIPS1997_1408}.}
These indices are all available in R packages, scagnostics [@HWscagR], mbgraphic [@mbgraphic] and minerva [@minerva]. The projection pursuit guided tour is available in the R package, tourr [@tourr].

@@

>>>>

[@Grimm2016] explored the behaviour of scagnostics for selecting variables, and proposed two more, based on smoothing splines that have some nicer properties. In addition the availability of another two indices based on information criteria, maximal and total information coefficient (MIC and TIC) [@Reshef1518] round out our collection of metrics. \footnote{It is interesting to note that entropy, closely related to the notion of mutual information, has previously been considered as a projection pursuit index when searching for interesting one-dimensional projections, see \cite{nason1992}, \cite{NIPS1997_1408}.}
These indices are all available in R packages [@rref]: scagnostics [@HWscagR], mbgraphic [@mbgraphic] and minerva [@minerva]. The projection pursuit guided tour is available in the R package, tourr [@tourr].

@@

In general we require that a good ppi should be smooth over geodesically interpolated projections, and be fast to calculate for dynamic viewing of the optimization with the guided tour. Note that there is a trade-off between smoothness requirements and the efficiency of the optization, and index functions sensitive to random small fluctuations may be viable in conjunction with an approriate optimization strategy, as noted above. Moreover, larger calculation times may be acceptable when we do not require observing the optimization in real-time, but instead record the guided tour which can be replayed once the optimization has converged.
